% Cover letter using letter.sty
\documentclass{letter} % Uses 10pt
%Use \documentstyle[newcent]{letter} for New Century Schoolbook postscript font
% the following commands control the margins:
\topmargin=-1in    % Make letterhead start about 1 inch from top of page 
\textheight=8in  % text height can be bigger for a longer letter
\oddsidemargin=0pt % leftmargin is 1 inch
\textwidth=6.5in   % textwidth of 6.5in leaves 1 inch for right margin

\begin{document}

\signature{James F. Jones}           % name for signature 
\longindentation=0pt                       % needed to get closing flush left
\let\raggedleft\raggedright                % needed to get date flush left
 
 
\begin{letter}{Ms. Keane, Ms. Lombardi\\
Athena Health
}


\begin{flushleft}
{\large\bf James F. Jones}
\end{flushleft}
\medskip\hrule height 1pt
\begin{flushright}
% The address might look better above the horizontal rule.  The reason I say this is that
% when I see an address on the right (not separated by anything from the text that follows),
% I get the impression that it's the address of the company you're writing to.
\hfill 2910 Saddlebrook Glen Drive, Cumming, GA, 30041\\
\hfill (678) 765-9529 / jay.f.jones@gmail.com
\end{flushright} 
\vfill % forces letterhead to top of page

\opening{Dear Ms. Keane and Lombardi:} 
 
\noindent 
I am writing today in regards to the software developer position
3325BR.

\noindent I have worked on the same project for 10 years and find
that I am looking for a new challenge and a chance to grow my 
skill-set and career.  As a child my parents worked
in the medical industry and as I grew up, I even considered the same
medical tract.  Instead though my calling to the "geekier" side
attracted me to computers.  When I saw the position for Software 
Developer in Alpharetta, I was immediately struck by the notion that 
I could continue my family's medical background using my software
design and programming skills.

In my current position with Arris I design and develop software
that runs on a world class Cable Modem Termination System (CMTS).  This
system is responsible for providing reliable phone, television, and Internet
service to many customers of Comcast, Time-Warner, and other 
cable companies. During my time with Arris I have developed software
for the CMTS using the C and C++ languages and have provided tools and test 
suites for our C/C++ code using Java and Perl.

I love learning the nuances of computer languages and enjoy 
when I am able to design and make tools.  It is an even greater
feeling of accomplishment when I can then refine that tool so that it is a
pleasure to be used by colleagues and customers alike.

In the fifteen years that I have worked for Arris/Nortel I have weathered 
the dot-com bust and the recession.  Over this time I have been relocated twice 
to provide expertise and training to new groups within the organization. 
 
\noindent I would appreciate the opportunity to discuss the Software 
Development position (3325BR) with you at a date, time, and place of your
convenience. I can be contacted by phone (678-765-9529) or e-mail (jay.f.jones@gmail.com).

\noident Thank you for your consideration.
 
\closing{Sincerely yours,} 


 
% \encl{}  				% Enclosures

\end{letter}
 

\end{document}






