% LaTeX resume using res.cls
\documentclass[line,margin]{res} 
\usepackage{helvetica} % uses helvetica postscript font (download helvetica.sty)
%\usepackage{newcent}   % uses new century schoolbook postscript font 
                
% \sl will be bold italic in New Century Schoolbook (or
% any postscript font) and just slanted in
% Computer Modern (default) font

\begin{document}

\name{James F. Jones}
% \address used twice to have two lines of address
\address{2910 Saddlebrook Glen Dr.}
\address{Cumming, GA 30041}

\begin{resume}
\section{ABOUT ME} I love to create!  It is the best feeling when I am able to provide tools and insight that helps others 
                reach their objectives faster and with better quality. I am patient and understand how to balance short
                term needs while working towards long term goals.

\section{EXPERIENCE} {\sl Staff Engineer} \hfill since 2003 \\
                Arris Incorporated, Lisle, Il and Suwanee, GA \\
                C4/E6000 CMTS CLI Team
                 \begin{itemize}  \itemsep -2pt % reduce space between items
                 \item Design and implementation of Cisco compatible command line interface in C++ on VxWorks.
                 \item Implementation of DOCSIS Device Classes feature.
                 \item Introduced TDD and automated developer test rig using Perl and Ruby.
                 \item Replaced inefficient and aging costly tool-set using Java and Netbeans.
                 \item Worked on fault tolerant and system redundancy using Rhapsody.
                 \end{itemize}

                {\sl Senior Engineer/Team Lead} \hfill 1997 - 2002 \\
                Nortel, RTP, NC \\
                Signaling Service Group SS7
                 \begin{itemize}  \itemsep -2pt % reduce space between items
                 \item Assisted in design and implementation of fault handling and system fail-over for Nortel's Signaling System 7 product line.
                 \item Introduced "Double Choco Latte" for bug tracking. 
                 \item ISO 9001 training and documentation team member.
                 \end{itemize}
                
                {\sl Member of Scientific Staff} \hfill 1997 - 2002 \\
                BNR - Nortel, RTP, NC \\
                DMS-10
                 \begin{itemize}  \itemsep -2pt % reduce space between items
                 \item Designed and implemented ISDN display protocol using SL-1.
                 \item Y2K bug fix.
                 \end{itemize}

%                {\sl Conscripted child labor for "Medical Parents"} \hfill 1981 - 1986 \\
%                Lexington Medical Center 
%                 \begin{itemize}  \itemsep -2pt % reduce space between items
%                 \item Worked as "administrative assistant" for my father.
%                 \item Made it through too many Spaghetti dinners while my parents discussed that days "interesting" medical cases.
%                 \item Using C=64 computer, Quick Brown Fox cartridge, and a tape datasette, transcribed lecture notes from my fathers nursing classes.
%                 \end{itemize}
 
\section{COMPUTER SKILLS} {\sl Languages \& Software:} C/C++, Perl, Java,
                Ruby, Clearcase, Git, GNU, Netbeans, Vim \\
                {\sl Operating Systems:} Windows, Mac OS X, Unix, VxWorks \\ 
                {\sl Protocols:} DHCP, TCP/UDP, DOCSIS 2.0, DOCSIS 3.0
 
\section{EDUCATION} {\sl Bachelor of Science,} Computer Engineering \\
                    {\sl Bachelor of Science,} Electrical Engineering \\
                North Carolina State University, 1996 \\
                Vice-President, Eta Kappa Nu, 1995 \\ 
                President, Eta Kappa Nu, 1996 \\
 
\section{EXTRA-CURRICULAR ACTIVITIES}             
             I am a 4th KYU (White) Belt Aikido (Aikido student). \\
             Board and Video Game Geek. \\
             Reading "Hacker News" and investigating different software development/test paradigm.

\end{resume}
\end{document}

